A First Effort for a Distributed Segment-based Approach on Self-Assembled Nano Networks

### 2013-09-20 trunk/PAPER/disr.tex
Final fix to typos

\subsection{Basic Idea}
The main concept behind of the original SR approach is the
\emph{segment}: a segment is basically a path of consecutive node and
links. A segment $S_1$ starts with a link attached to a node which
belongs to different segment $S_2$, ending with a link attached to a
node belonging to a different segment $s_3$. In other words, a segment
a path between connecting two other different segments.A exception is
the first segment estabilished in the network, called \emph{starting
segment} which is  a loop beginning/ending on a particular node
defined as \emph{bootstrap node}.
The idea is to partition the network in a set of disjoint segments, and then
placing a turn restriction within each segment. It has been proved~\cite{mejia_ipdps06}
that such a set of turn prohibitions guarantees dealock freedom and
while preserving connectivity of the network.

@@

As regards packet\_type, we can have the following control packets:
\begin{itemize}
\item{\texttt{STARTING\_SEGMENT\_REQUEST}}: Injected by the bootstrap
node to when searching for the first segment. 
\item{\texttt{STARTING\_SEGMENT\_CONFIRM}}: used when estabilishing
the starting  segment. 
\item{\texttt{SEGMENT\_REQUEST}}: used to search candidates for a segment (not the
first)
\item{\texttt{SEGMENT\_CONFIRM}}: used to estabilish a segment. 
\item{\texttt{SEGMENT\_CANCEL}}: used to cancel the process of searching a segment along a
specific link.
\end{itemize}

@@

\item{\textbf{Injecting bootstrap request}}: all nodes have a initial
\emph{DBS} status \emph{Free}, except for a
 node with status \emph{Bootstrap}, set by some signal from an
upper layer via (a). When starting, this bootstrap node 
changes its status to \emph{ActiveSearching} (b), injecting a
\texttt{STARTING\_SEGMENT\_REQUEST} across one of its free links.

\item{\textbf{Flooding}}: Each node receiving a \texttt{STARTING\_SEGMENT\_REQUEST},
if $Free$ forwards it to its free links using a flooding mechanism and
becoming $CandidateStarting$ (g).
Each of its free links is then marked as \emph{tvisited} with the segment id
associated to the request. Note that a node that has already received a
\texttt{STARTING\_SEGMENT\_REQUEST} packet can simply ignore further packets
associated to the same request, having already contributed to the
flooding. 
%Note also that each of these packets has a max\_segment\_hops
%field to prevent packets from travelling undefinitively.

\item{\textbf{Confirming the Starting Segment}}: when the \texttt{STARTING\_SEGMENT\_REQUEST} packet reaches
the bootstrap node (from a different link, of course), the starting
segment is found. Then the boostrap node sends back a \texttt{STARTING\_SEGMENT\_CONFIRM}
packet along the link from which it received the
\texttt{STARTING\_SEGMENT\_REQUEST} and becomes $Assigned$ (c). Each
node receiving the confirm do same by changing its own status
to \emph{Assigned} (l). So the confirmation packet is sent back from
node to node and the starting segment is created.

@@

\item{\textbf{Setup of a segment}}: The find process is successfull
when an already \emph{Assigned} node receives the
\texttt{SEGMENT\_REQUEST} packet. Then, a \texttt{SEGMENT\_CONFIRM} is
sent back along the path that originated the request (e), while the
node remain $Assigned$ (since it could confirm more segments). Each node
previously set as $Candidate$ for that segment id, when receiving the
confirm packet changes its status to $Assigned$ (m) and forwards back
the same confirm until it reaches the initator of the request, which
changes from $ActiveSearching$ to $Assigned$ (c).

>>>>

\subsection{Basic Idea}
The main concept behind of the original SR approach is the
\emph{segment}: a segment is basically a path of consecutive node and
links. A segment $S_1$ starts with a link attached to a node which
belongs to different segment $S_2$, ending with a link attached to a
node belonging to a different segment $s_3$. In other words, a segment
a path between connecting two other different segments.A exception is
the first segment established in the network, called \emph{starting
segment} which is  a loop beginning/ending on a particular node
defined as \emph{bootstrap node}.
The idea is to partition the network in a set of disjoint segments, and then
placing a turn restriction within each segment. It has been proved~\cite{mejia_ipdps06}
that such a set of turn prohibitions guarantees deadlock freedom and
while preserving connectivity of the network.

@@

As regards packet\_type, we can have the following control packets:
\begin{itemize}
\item{\texttt{STARTING\_SEGMENT\_REQUEST}}: Injected by the bootstrap
node to when searching for the first segment. 
\item{\texttt{STARTING\_SEGMENT\_CONFIRM}}: used when establishing
the starting  segment. 
\item{\texttt{SEGMENT\_REQUEST}}: used to search candidates for a segment (not the
first)
\item{\texttt{SEGMENT\_CONFIRM}}: used to establish a segment. 
\item{\texttt{SEGMENT\_CANCEL}}: used to cancel the process of searching a segment along a
specific link.
\end{itemize}

@@

\item{\textbf{Injecting bootstrap request}}: all nodes have an initial
\emph{DBS} status \emph{Free}, except for a
 node with status \emph{Bootstrap}, set by some signal from an
upper layer via (a). When starting, this bootstrap node 
changes its status to \emph{ActiveSearching} (b), injecting a
\texttt{STARTING\_SEGMENT\_REQUEST} across one of its free links.

\item{\textbf{Flooding}}: Each node receiving a \texttt{STARTING\_SEGMENT\_REQUEST},
when $Free$ forwards it to its free links using a flooding mechanism and
becoming $CandidateStarting$ (g).
Each of its free links is then marked as \emph{tvisited} with the segment id
associated to the request. Note that a node that has already received a
\texttt{STARTING\_SEGMENT\_REQUEST} packet can simply ignore further packets
associated to the same request, having already contributed to the
flooding. 
%Note also that each of these packets has a max\_segment\_hops
%field to prevent packets from travelling undefinitively.

\item{\textbf{Confirming the Starting Segment}}: when the \texttt{STARTING\_SEGMENT\_REQUEST} packet reaches
the bootstrap node (from a different link, of course), the starting
segment is found. Then the bootstrap node sends back a \texttt{STARTING\_SEGMENT\_CONFIRM}
packet along the link from which it received the
\texttt{STARTING\_SEGMENT\_REQUEST} and becomes $Assigned$ (c). Each
node receiving the confirm do same by changing its own status
to \emph{Assigned} (l). So the confirmation packet is sent back from
node to node and the starting segment is created.

@@

\item{\textbf{Setup of a segment}}: The find process is successful
when an already \emph{Assigned} node receives the
\texttt{SEGMENT\_REQUEST} packet. Then, a \texttt{SEGMENT\_CONFIRM} is
sent back along the path that originated the request (e), while the
node remain $Assigned$ (since it could confirm more segments). Each node
previously set as $Candidate$ for that segment id, when receiving the
confirm packet changes its status to $Assigned$ (m) and forwards back
the same confirm until it reaches the initiator of the request, which
changes from $ActiveSearching$ to $Assigned$ (c).
